### 2013-09-13 discussion.tex
notes added

Discussion text will go here.

>>>>

\begin{itemize}
    \item BPH and PCa can heavily compromise ability to see zones.  No healthy prostates were studied, which would have made this analysis easier; however, the prostate of the older man, which would be in our screening population, is not that of the healthier, younger male, making analysis in that population less meaningful.
\end{itemize}
